---
title: "p8105_hw1_rt2640"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

Question 1
This code chunk includes creating a data frame with sample size of 10 variables randomly selected from a normal distribution with values greater than 0. It also includes creating a character vector and a factor vector to create 3 levels and taking a mean of each of the vectors in the data frame.

```{r question_1}

q1_df = tibble(
  vec_numeric = rnorm(10),
  vec_numeric_logical = vec_numeric > 0,
  vec_char = vector(length = 10),
  vec_factor = factor(c("A","B","C","A","B","C","A","B","C","A"))
)
```

```{r question_1_mean}

mean1 = mean(pull(q1_df,var = vec_numeric))
mean2 = mean(pull(q1_df, var = vec_numeric_logical))
mean3 = mean(pull(q1_df , var = vec_char))
mean4 = mean(pull(q1_df , var = vec_factor))

mean5 = mean(as.numeric(pull(q1_df , var = vec_factor)))
```

Mean 1-4 are the means for the vectors from the original data frame.The mean for variables vec_numeric, vec_logical, and vec_character were calculated using the pull function to pull the variables from the data frames. Since vec_factor is a character variable, mean4 resulted in an error. Mean5 converts the vec_factor from a character variable to a numeric variable using the as.numeric function to successfully output the mean for the variable.




