---
title: "P8105_HW1_RT2640"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1
This code chunk includes creating a data frame with sample size of 10 variables randomly selected from a normal distribution with values greater than 0. It also includes creating a character vector and a factor vector to create 3 levels and taking a mean of each of the vectors in the data frame.

```{r question_1}
set.seed(2)
q1_df = tibble(
  vec_numeric = rnorm(10),
  vec_numeric_logical = vec_numeric > 0,
  vec_char = vector(length = 10),
  vec_factor = factor(c("A","B","C","A","B","C","A","B","C","A"))
)
```

```{r question_1_mean}

mean1 = mean(pull(q1_df,var = vec_numeric))
mean2 = mean(pull(q1_df, var = vec_numeric_logical))
mean3 = mean(pull(q1_df , var = vec_char))
mean4 = mean(pull(q1_df , var = vec_factor))

mean5 = mean(as.numeric(pull(q1_df , var = vec_factor)))
```

Mean 1-4 are the means for the vectors from the original data frame.The mean for variables vec_numeric, vec_logical, and vec_character were calculated using the pull function to pull the variables from the data frames.

1. mean1 = mean_vec_numeric = -0.07730
2. mean2 = mean_vec_numeric_logical = 0.4
3. mean3 = mean_vec_char = 0

Since vec_factor is a character variable, mean4 resulted in an error. Mean5 converts the vec_factor from a character variable to a numeric variable using the as.numeric function to successfully output the mean for the variable.

### Question 2 
This code chunk includes includes installing the palmerpenguins package and loading the penguins dataset along with a short description of the dataset.

```{r question_2_loading_dataset}

data("penguins", package = "palmerpenguins")

```

#### Summary of the data set 
##### Table 1

`r knitr::kable(summary(penguins))`
1. The data set includes `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
2. The data set includes variables penguin species, the island, the sex of the penguins, and the year the data was collected.
3. Other descriptive variables include bill length, bill depth, flipper length, and body mass as decribed in Table 1.
4. The mean flipper length of penguins in the given data set is `r round(mean(pull(penguins, var = flipper_length_mm),na.rm=TRUE),2)` mm.

This code chunk includes creating a scatterplot for flipper length vs bill length and saving the scatterplot.


```{r question_2_scatterplot}

library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm , y = flipper_length_mm , color = species)) + geom_point()

ggsave("./09272021_q2_penguins_species_scatterplot.jpeg")
```


